CommonMind Consortium: DLPFC

### 2020-09-18 combined_analysis/diff.networks.Rmd
Update diff networks

```{r sex.confounding, fig.width=5, fig.height=20}
form = ~ Reported_Gender + GABA + GLU + Olig + MgAs + ageOfDeath 
par(mfrow=c(2,2))
res = lapply( unique(METADATA$Institution), function(INST){
	i = METADATA$Institution == INST
	C = canCorPairs(form, METADATA[i,]) 
	plotCorrMatrix(C, main=INST)
})
```

@@

plot_enrich(df_module_enrich.Sex[1:10,], module) + ggtitle()

@@

@@

>>>>

```{r sex.confounding, fig.width=5, fig.height=4}
form = ~ Reported_Gender + GABA + GLU + Olig + MgAs + ageOfDeath 
par(mfrow=c(2,2))
res = lapply( unique(METADATA$Institution), function(INST){
	i = METADATA$Institution == INST
	C = canCorPairs(form, METADATA[i,]) 
	plotCorrMatrix(C, main=INST)
})
```

@@

```{r plot.enrich.Sex, fig.width=9}
figList = lapply( df_cohort2$Module[i], function(module){
	plot_enrich(df_module_enrich.Sex, module, 8) + ggtitle(module)
	})
plot_grid(plotlist = figList, ncol=1)
```

@@

```{r plot.enrich.Dx, fig.width=9}
figList = lapply( df_cohort2$Module[i], function(module){
	plot_enrich(df_module_enrich.Dx, module, 8) + ggtitle(module)
	})
plot_grid(plotlist = figList, ncol=1)
```

@@

```{r plot.enrich.Dx_Sex, fig.width=9}
figList = lapply( df_cohort2$Module[i], function(module){
	plot_enrich(df_module_enrich.Dx_Sex, module, 8) + ggtitle(module)
	})
plot_grid(plotlist = figList, ncol=1)
```
